### 2015-10-14 paper.tex
Mention the lower solidity to blame for weaker tip vortices; resolves #13
Add exp setup photo; resolves #5

Experiments were performed in the UNH tow/wave tank, a 36 m long facility with a
3.66 m wide by 2.44 m deep cross-section, capable of tow speeds up to 3 m/s,
pictured in Figure~\ref{fig:tow-tank}. The turbine was mounted in a frame built
from NACA 0020 struts, attached to the tow carriage by four linear bearings,
which transfer all streamwise force to a pair of S-beam load cells. The turbine
shaft RPM was controlled by a servo motor system, which allowed prescription of
the turbine tip speed ratio. The load torque was measured by an inline rotary
torque transducer and a load cell mounted at a fixed distance from the servo
motor, providing a redundant measurement. Turbine shaft angle was measured using
the servo drive's emulated encoder output, set to $10^5$ counts per turbine
shaft revolution. Carriage speed, and therefore inflow velocity was measured
using a linear encoder with 10 $\mu$m resolution. All of these
performance-related quantities were sampled as 2 kHz, while the tow tank's
motion controller provided redundant measurements of the carriage speed and
turbine angular velocity sampled at 1 kHz. Turbine wake measurements at 1 meter
downstream were measured with a Nortek Vectrino+ acoustic Doppler velocimeter,
sampling at 200 Hz. A drawing of the experimental setup is shown in
Figure~\ref{fig:exp-setup}.

\begin{figure}[h]
\caption{Photos of the UNH towing tank and turbine test bed.} 
\label{fig:tow-tank}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[clip,trim=0.01in 0 0 0,
width=\textwidth]{figures/tank_cross_section}
\caption{{\bf Experimental setup.} Illustration of the experimental setup.}
\label{fig:exp-setup}
\end{figure}

@@

The mean velocity field at a tip speed ratio $\lambda=3.1$, 1 m downstream
($x/D=0.93$) is plotted in Fig.~\ref{fig:meancontquiv}. The mean streamwise
velocity deficit is markedly more symmetric than that of the UNH-RVAT, with
lower acceleration around the turbine thanks to lower rotor drag coefficient and
blockage ratio \cite{Bachant2015-JoT}. We also see that the effects of blade tip
vortex shedding are relatively weaker.

>>>>

Experiments were performed in the UNH tow/wave tank, a 36 m long facility with a
3.66 m wide by 2.44 m deep cross-section, capable of tow speeds up to 3 m/s,
pictured in Figure~\ref{fig:tow-tank}. The turbine was mounted in a frame built
from NACA 0020 struts, attached to the tow carriage by four linear bearings,
which transfer all streamwise force to a pair of S-beam load cells. The turbine
shaft RPM was controlled by a servo motor system, which allowed prescription of
the turbine tip speed ratio. The load torque was measured by an inline rotary
torque transducer and a load cell mounted at a fixed distance from the servo
motor, providing a redundant measurement. Turbine shaft angle was measured using
the servo drive's emulated encoder output, set to $10^5$ counts per turbine
shaft revolution. Carriage speed, and therefore inflow velocity was measured
using a linear encoder with 10 $\mu$m resolution. All of these
performance-related quantities were sampled as 2 kHz, while the tow tank's
motion controller provided redundant measurements of the carriage speed and
turbine angular velocity sampled at 1 kHz. Turbine wake measurements at 1 meter
downstream were measured with a Nortek Vectrino+ acoustic Doppler velocimeter,
sampling at 200 Hz. A photo and drawing of the experimental setup are shown in
Fig.~\ref{fig:exp-setup-photo} and Fig.~\ref{fig:exp-setup}, respectively.

\begin{figure}[h]
    \centering

    \includegraphics[width=0.95\textwidth]{figures/exp-setup-photo}

    \caption{\textbf{Experimental setup.} Photo of the UNH tow tank and
        turbine test bed with RM2 installed.}

    \label{fig:exp-setup-photo}
\end{figure}

\begin{figure}[h]
    \centering

    \includegraphics[clip,trim=0.01in 0 0 0,
    width=\textwidth]{figures/tank_cross_section}

    \caption{{\bf Experimental setup.} Illustration of the experimental setup.}

    \label{fig:exp-setup}
\end{figure}

@@

The mean velocity field at a tip speed ratio $\lambda=3.1$, 1 m downstream
($x/D=0.93$) is plotted in Fig.~\ref{fig:meancontquiv}. The mean streamwise
velocity deficit is markedly more symmetric than that of the UNH-RVAT, with
lower acceleration around the turbine thanks to lower rotor drag coefficient and
blockage ratio \cite{Bachant2015-JoT}. We also see that the effects of blade tip
vortex shedding are relatively weaker, which is likely an effect of the RM2's
lower solidity and tapered blades.
